---
title: 'Homework 2 - Research in Health Economics'
author: "Alexia Witthaus Viñé"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
    toc_depth: '2'
  prettydoc::html_pretty:
    df_print: kable
    highlight: vignette
    theme: lumen
  html_document:
    df_print: paged
---
```{r echo = FALSE}
load("image.Rdata")
library(lemon)
knit_print.data.frame <- lemon_print
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

# Question 1 


```{r hosptime, fig.name = "Hopsitals that files more than one report"}
graph_1
```

# Question 2 

There are `r format(unique_hospitals, big.mark = ",")` unique hospitals in the data set. 

# Question 3

```{r}
graph_3
```

# Question 4 

```{r}
graph_4 
```

# Question 5 

The average price for a hospital without penalty is `r round(table_5$price[1],2)`, while the average price of a hospital with penalty is `r round(table_5$price[2],2)`. 



# Question 6 


```{r dupreports, render = lemon_print, fig.cap = "Duplicate reports"}
table_6 
```


# Question 7 

```{r, render = lemon_print}
table_7
```



# Question 8 

The results above are identical to each other.  


# Question 9 

I don't think I have a casual effect above, since I have only controlled for a few variables (quartiles, penalty). There are likely other variables such as the competition mentioned in class, not included in the estimators that bias the result, as hospitals with high competition may tend to have less penalties and higher prices. This would make that the groups we are comparing to each other are systematically different from each other, and we would be obtaining bias results. 

# Question 10

The hardest part for me was getting the data this time, as I had to do it manually. Apart from this, I have had a hard time figuring out how to code what we learned in class in regards to IPW. I understood the theory, but had a hard time putting it into practice.  


