---
title: "Research in Health Economics- Homework 2"
author: "Alexia Witthaus Viñé"
date: "2023-02-11"
output: pdf_document
---

```{r echo = FALSE}
load("image.Rdata")
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

# Question 1 

```{r}
graph_1
```

# Question 2 

There are `r unique_hospitals` unique hospitals in the data set. 

# Question 3

```{r}
graph_3
```

# Question 4 

```{r}
graph_4 
```

# Question 5 

```{r}
table_5
```

# Question 6 

```{r}
table_6 
```


# Question 7 

For KNN regression with inverse variance based on quartiles of bed size 
```{r}
nn_weight$est
```


For KNN regression with Mahalanobis distance based on quartiles of bed size
```{r}
nn_mahala$est
```

For inverse propensity weighting 
```{r}
delta
```

For regression
```{r}
reg_ate
```


# Question 8 

I am pretty sure I made a mistake above, but I would expect the results to be similar, given that we are controlling for the same variables in all the estimators. 


# Question 9 

I don't think I have a casual effect above, since I have only controlled for a few variables (quartiles, penalty). There are likely other variables such as the competition mentioned in class, not included in the estimators that bias the result. 

# Question 10

The hardest part for me was getting the data this time, as I had to do it manually. Apart from this, I have had a hard time figuring out how to code what we learned in class in regards to IPW. I understood the theory, but had a hard time putting it into practice. 


















