---
title: "Research in Health Economics- Homework 2"
author: "Alexia Witthaus Viñé"
date: "2023-02-14"
output: pdf_document
---
```{r echo = FALSE}
load("image.Rdata")
library(lemon)
knit_print.data.frame <- lemon_print
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

# Question 1 

```{r}
graph_1
```

# Question 2 

There are `r unique_hospitals` unique hospitals in the data set. 

# Question 3

```{r}
graph_3
```

# Question 4 

```{r}
graph_4 
```

# Question 5 

The average price for a hospital without penalty is `r round(table_5$price[1],2)`, while the average price of a hospital with penalty is `r round(table_5$price[2],2)`. 


# Question 6 

```{r, render = lemon_print}
table_6 
```


# Question 7 

 * The estimate of the ATE for KNN regression with inverse variance is  **`r round(nn_weight$est,2) `**


* The estimate of the ATE for KNN regression with Mahalanobis distance is **`r round(nn_mahala$est,2)`**


* The estimate of the ATE for inverse propensity weighting is **`r round(delta,2)`**

* The estimate of the ATE using regression is  **`r round(reg_ate,2)`**


# Question 8 

I am pretty sure I made a mistake above, but I would expect the results to be similar, given that we are controlling for the same variables in all the estimators. 


# Question 9 

I don't think I have a casual effect above, since I have only controlled for a few variables (quartiles, penalty). There are likely other variables such as the competition mentioned in class, not included in the estimators that bias the result. 

# Question 10

The hardest part for me was getting the data this time, as I had to do it manually. Apart from this, I have had a hard time figuring out how to code what we learned in class in regards to IPW. I understood the theory, but had a hard time putting it into practice.  
